### 2014-03-16 src/introduction.Rnw
Fixes from Amin

However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the field
has a serious lacuna in large scale research, both in the size of the
programs studied, and in the number and diversity of programs, which
reduces our confidence in all results. This is true for selective
mutation studies, studies in sampling, and also for comparatively
newer studies that attempt to combine methods. This is particularly
worrisome if mutation analysis is to gain wider acceptance among
testing professionals. Further, quite a few of the influential
studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
were conducted on older programming languages such as Fortran, with
operators specific to the language, and are not directly applicable to
newer languages such as Java. Finally, with bytecode based mutation
engines like PIT~\cite{pitest} and Javalanche~\cite{javalanche}
(a \textit{do faster} approach for eliminating
the compilation step to gain execution speed), operators based on
source code modification are no longer applicable, and their
equivalents in bytecode need to be identified and compared with other
approaches. A detailed discussion of these issues can be found in
Section~\ref{sec:related}.

We have attempted to rectify this situation with a large scale study
of real world programs.  As detailed in Section~\ref{sec:methodology},
we sample 188 Java programs from Github, with size ranging from 50 LOC
to 100 KLOC, which allows widely applicable statistical inferences to
be made. We provide the results from running both the original
project's (presumably human-generated) test suites and also
automatically generated test suites using random testing, increasing
the applicability of our findings to both testers in traditional
development who are interested in applying mutation analysis to suite
evaluation and to researchers who seek to compare test suites quickly to evaluate testing techniques.

@@

\item We compare a much large number of mutant reduction strategies
than previous studies. We compare with respect to the predictive power
(correlation with the full mutation score), expected mutant reduction,
and the stability of the amount of mutant reduction expected. Our
sampling strategies include some that were suggested by other
researchers, as well as a few novel strategies not previously considered.

>>>>

However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the field
has a serious lacuna in large scale research, both in the size of the
programs studied, and in the number and diversity of programs, which
reduces our confidence in all results. This is true for selective
mutation studies, sampling studies, and also for comparatively
newer studies that attempt to combine methods. This is particularly
worrisome if mutation analysis is to gain wider acceptance among
testing professionals. Further, quite a few of the influential
studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
were conducted on older programming languages such as Fortran, with
operators specific to the language, and are not directly applicable to
newer languages such as Java. Finally, with bytecode based mutation
engines like PIT~\cite{pitest} and Javalanche~\cite{javalanche}
(a \textit{do faster} approach for eliminating
the compilation step to gain execution speed), operators based on
source code modification are no longer applicable, and their
equivalents in bytecode need to be identified and compared with other
approaches. A detailed discussion of these issues can be found in
Section~\ref{sec:related}.

We have attempted to rectify this situation with a large scale study of real
world programs.  As detailed in Section~\ref{sec:methodology}, we sample
188 Java programs from Github, with size ranging from 50 LOC to 100 KLOC,
which should allow widely applicable statistical inferences to be made. We
provide the results from running both the original project's (presumably
human-generated) test suites and also automatically generated test suites
using random testing, increasing the applicability of our findings to both
testers in traditional development who are interested in applying mutation
analysis to suite evaluation and to researchers who seek to compare test
suites quickly to evaluate testing techniques.

@@

\item We compare a much larger number of mutant reduction strategies
than previous studies. We compare with respect to the predictive power
(correlation with the full mutation score), expected mutant reduction,
and the stability of the amount of mutant reduction expected. Our
sampling strategies include some that were suggested by other
researchers, as well as a few novel strategies not previously considered.

### 2014-03-16 src/methodology.Rnw
Fixes from Amin

\section{Methodology} \label{sec:methodology} Our selection of
programs was driven by a few overriding concerns. Our primary
requirement was that our results had to be as widely applicable as
possible for real-world programs. Secondly, we strived for a
statistically significant result, reducing the number of variables
present in the experiments. For this reason we chose a random sample
of Java projects from Github~\cite{github} that use the popular
maven~\cite{maven} build system, following the methodology we used
previously in an ICSE 2014 paper~\cite{gopinath2014code}. As in that
work, we utilize two kinds of of test suites: the original test suites
present in a limited number of projects, and automatically generated
test suites from Randoop~\cite{randoop}.  Due to limited resources, we
had to further reduce the programs and test suites to those that could
finish mutation analysis in 10 minutes. From this set of test suites,
we sampled 107 suites each for both original and Randoop generated
test suites. Since there was some overlap between projects with
original test suites, and those with generated test suites, we had 81
unique projects each in both sets. The remaining 26 projects had both
flavors of test suites.

We ran mutation analysis on this set of projects using
PIT\cite{pitest}. However, since the operators provided by PIT are
limited, we extended PIT to provide newer operators that are similar to
operators provided by other mutation systems. The set of operators that
we used is provided in Table~\ref{tbl:pitop}. Figure~\ref{fig:op} shows
both the distribution of mutants and the relative detection rates of each
mutation operator for our projects. In the figure, there are two box-plots
corresponding to each mutation operator on the Y-axis. The black box represents
the relative frequency of the particular mutation operator in the total
mutants \textit{produced}. For example, for projects in the (Randoop) generated set,
the operator \pitnvmc contributed about 34\% of the total number of mutants
produced while \pitrv contributed about 7\%. Similarly, the blue shaded
box-plot represents the relative frequency of particular mutation operator
in the total mutants \textit{detected}. For example, \pitnvmc contribution
in the detected mutants was 23\% while that of \pitrv was 15\%.

For a detailed description of each mutant type, please refer to PIT documentation~\cite{pitmut}.
PIT was also modified to provide random selection of mutants according
to various criteria. Finally, to remove random noise, each criteria
described was run four times, and the results averaged to produce
the final result.

@@

One of the criteria we sampled was \textit{statement deletion}.
Since we use PIT, which is a bytecode based mutation engine, implementing direct equivalent of
source code statement deletion is very hard. We were able to approximate statement deletion
by combining different bytecode operators, as explained in Subsection~\ref{subsec:stmtdel}.

>>>>

\section{Methodology} \label{sec:methodology} Our selection of
programs was driven by a few overriding concerns. Our primary
requirement was that our results had to be as widely applicable as
possible for real-world programs. Secondly, we strived for a
statistically significant result, reducing the number of variables
present in the experiments. For this reason we chose a random sample
of Java projects from Github~\cite{github} that use the popular
maven~\cite{maven} build system, following the methodology we used
previously in an ICSE 2014 paper~\cite{gopinath2014code}. As in that
work, we utilize two kinds of of test suites: the original test suites
present in a limited number of projects, and automatically generated
test suites from Randoop~\cite{randoop}. From this set of test suites,
After eliminating those that took too long to finish, we sampled 107
suites each for both original and Randoop generated test suites,
Since there was some overlap between projects with
original test suites, and those with generated test suites, we had 81
unique projects each in both sets. The remaining 26 projects had both
flavors of test suites.

We ran mutation analysis on this set of projects using
PIT\cite{pitest}. However, since the operators provided by PIT are
limited, we extended PIT to provide newer operators that are similar to
operators provided by other mutation systems. The set of operators that
we used is provided in Table~\ref{tbl:pitop}. Figure~\ref{fig:op} shows
the distribution of mutants and the relative detection rates of each
mutation operator for our projects. In the figure, there are two box-plots
corresponding to each mutation operator on the Y-axis. The black box represents
the relative frequency of the particular mutation operator in the total
mutants \textit{produced}. For example, for projects in the (Randoop) generated set,
the operator \pitnvmc contributed about 34\% of the total number of mutants
produced while \pitrv contributed about 7\%. Similarly, the blue shaded
box-plot represents the relative frequency of particular mutation operator
in the total mutants \textit{detected}. For example, \pitnvmc contribution
in the detected mutants was 23\% while that of \pitrv was 15\%.

For a detailed description of each mutation operator, please refer to PIT documentation~\cite{pitmut}.
PIT was also modified to provide random selection of mutants according
to various criteria.
Finally, to remove random noise, each criteria
described was run four times, and the results averaged to produce
the final result.

@@

### 2014-03-16 src/related.Rnw
Fixes from Amin

\section{Related Work}
\label{sec:related}
There are several approaches to reducing the cost of mutation analysis.
These were categorized by Offutt and Untch~\cite{offutt2001mutation}
into three approaches: do \textit{fewer}, \textit{smarter}, and \textit{faster}.
The \textit{do fewer} approaches includes selective mutation and mutant sampling,
while weak mutation, parallelization of mutation analysis, and space/time trade-offs
are grouped under the umbrella of \textit{do smarter}. Finally
\textit{do faster} approaches include mutant schema generation methods,
code patching etc.

@@

A number of studies in the past have looked at the relative merits of operator
selection and random sampling criteria, starting with Wong and Mathur in
1995~\cite{wong1995reducing}. They compared x\% selection of each mutant type
with operator selection using just two mutation operators, and found that both
achieved similar accuracy and reduction (80\%).

@@

Zhang et al.~\cite{zhang2010operator} compared operators based mutant
selection techniques proposed in a set of
papers~\cite{barbosa2001toward,siami2008sufficient,offutt1996anexperimental}
to random mutant sampling. They found that none of the selection
techniques are superior to random sampling, with the same number of
mutants. They also found that uniform sampling of mutations is more effective
for larger subjects compared to equal sampling of mutation operators
and the reverse is true for smaller subjects.

@@

Some studies have tried to find the set of \emph{sufficient mutation
operators} that reduce the cost of mutation but maintain correlation
with the full mutation score. Offutt et al.~\cite{offutt1993experimental}
suggested an $n$-selective approach with step-by-step removal of operators
with most numerous mutations. Barbosa et al.\cite{barbosa2001toward}
provided a set of guidelines for selecting such mutation operators.
Namin et al.\cite{namin2006finding,siami2008sufficient} formulated
the problem as a variable reduction problem in statistics, and
found that just 28 out of 108 operators in Proteum were sufficient.

>>>>

\section{Related Work}
\label{sec:related}
There are several approaches to reducing the cost of mutation analysis.
These were categorized by Offutt and Untch~\cite{offutt2001mutation}
into three approaches: do \textit{fewer}, \textit{smarter}, and \textit{faster}.
The \textit{do fewer} approaches include selective mutation and mutant sampling,
while weak mutation, parallelization of mutation analysis, and space/time trade-offs
are grouped under the umbrella of \textit{do smarter}. Finally
\textit{do faster} approaches include mutant schema generation methods,
code patching etc.

@@

A number of studies in the past have looked at the relative merits of operator
selection and random sampling criteria. Wong et al.~\cite{wong1995reducing}
compared x\% selection of each mutant type
with operator selection using just two mutation operators, and found that both
achieved similar accuracy and reduction (80\%).

@@

Zhang et al.~\cite{zhang2010operator} compared operator based mutant
selection techniques to random mutant sampling. They found that none of
the selection techniques are superior to random sampling, with the same
number of mutants. They also found that uniform sampling of mutations is
more effective for larger subjects compared to equal sampling of mutation
operators and the reverse is true for smaller subjects.

@@

Some studies have tried to find the set of \emph{sufficient mutation
operators} that reduce the cost of mutation but maintain correlation
with the full mutation score. Offutt et al.~\cite{offutt1993experimental}
suggested an $n$-selective approach with step-by-step removal of operators
with most numerous mutations. Barbosa et al.\cite{barbosa2001toward}
provided a set of guidelines for selecting such mutation operators.
Namin et al.\cite{namin2006finding,siami2008sufficient} formulated
the problem as a variable reduction problem, and
found that just 28 out of 108 operators in Proteum were sufficient.
